An Experimental Evaluation of Hybrid Querying on Vectors (EA\&B)

### 2025-07-17 VLDB2026/main.tex
update fig

	\subsection{Index Organization in Hybrid ANN Search}

@@

		% 上面的图例，居中并可通过 hspace 调整左右位置
		\hspace*{16pt} % 可调整的参数，负值左移，正值右移，例如 -20pt 或 20pt
		\includegraphics[width=0.92\columnwidth]{figures/indexData/legend_only.pdf} % 图例图片路径

@@

			\includegraphics[width=0.95\linewidth]{figures/indexData/exp_7_build_time_comparison_query1.pdf}
			\caption{Index construction time}
			\label{fig:build_time_comparison_query1}
		\end{subfigure}

@@

			\includegraphics[width=0.95\linewidth]{figures/indexData/exp_7_memory_mb_comparison_query1.pdf}
			\caption{Peak memory usage}
			\label{fig:memory_mb_comparison_query1}
		\end{subfigure}

@@

			\includegraphics[width=0.95\linewidth]{figures/searchMem/memory_comparison.pdf}
			\caption{Search memory usage}
			\label{fig:memory_mb_comparison_query1}
		\end{subfigure}

		%		\caption{Time and space overhead of attribute filtering index construction}
		\caption{Time and space overhead of index construction}
		\label{fig:build_index_comparison}
	\end{figure}

@@

		\hspace*{11pt}
		% 放大的图例（占满单栏）
		\includegraphics[width=0.90\columnwidth]{figures/indexData/rangeFilter_legend_only.pdf}

@@

		% 三图横排
		\begin{subfigure}[t]{0.32\columnwidth}
			\centering
			\captionsetup{font=small}

			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_build_time_comparison_query.pdf}
			\caption{\footnotesize Construction time}
			\label{fig:rangeFilter_build_time}
		\end{subfigure}
		\hfill
		\begin{subfigure}[t]{0.32\columnwidth}
			\centering

			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_index_size_mb_comparison_query.pdf}
			\caption{\footnotesize Index size}
			\label{fig:rangeFilter_index_size_mb}
		\end{subfigure}
		\hfill
		\begin{subfigure}[t]{0.32\columnwidth}
			\centering

			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_memory_mb_comparison_query.pdf}
			\caption{\footnotesize Peak memory usage}
			\label{fig:rangeFilter_memory_mb}
		\end{subfigure}

		%		\caption{Time and space overhead of range filtering index construction}
		\caption{Time and space overhead of index construction}
		\label{fig:rangeFilter_build_index_comparison}
	\end{figure}

>>>>

%	\subsection{Index Organization in Hybrid ANN Search}
	\subsection{Index Organization in Hybrid Query}

@@

		% 上面的图例，居中并可通过 hspace 调整左右位置
		\hspace*{10pt} % 可调整的参数，负值左移，正值右移，例如 -20pt 或 20pt
		\includegraphics[width=0.95\columnwidth]{figures/indexData/legend_only.pdf} % 图例图片路径

@@

			\includegraphics[width=0.95\linewidth]{figures/indexData/exp_7_build_time_comparison_query1.pdf}
			\caption{Construction time}
			\label{fig:build_time_comparison_query1}
		\end{subfigure}

@@

			\includegraphics[width=0.95\linewidth]{figures/indexData/exp_7_memory_mb_comparison_query1.pdf}
			\caption{Build peak memory }
			\label{fig:search_memory_mb_comparison}
		\end{subfigure}

@@

			\includegraphics[width=0.95\linewidth]{figures/searchMem/label_memory_comparison.pdf}
			\caption{Search peak memory}
			\label{fig:build_memory_mb_comparison}
		\end{subfigure}

		%		\caption{Time and space overhead of attribute filtering index construction}
		\caption{\textcolor{violet}{Time and space overhead}}
		\label{fig:build_index_comparison}
	\end{figure}

@@

		\hspace*{5pt}
		% 放大的图例（占满单栏）
		\includegraphics[width=0.98\columnwidth]{figures/indexData/rangeFilter_legend_only.pdf}

@@

		% 三图横排
		\begin{subfigure}[t]{0.49\columnwidth}
			\centering
			\captionsetup{font=small}
			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_build_time_comparison_query.pdf}
			\caption{\footnotesize Construction time}
			\label{fig:rangeFilter_build_time}
		\end{subfigure}
		\hfill
		\begin{subfigure}[t]{0.49\columnwidth}
			\centering
			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_index_size_mb_comparison_query.pdf}
			\caption{\footnotesize Index size}
			\label{fig:rangeFilter_index_size_mb}
		\end{subfigure}
		\hfill
		\begin{subfigure}[t]{0.49\columnwidth}
			\centering
			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_index_size_mb_comparison_query.pdf}
			\caption{\footnotesize Build peak memory}
			\label{fig:rangeFilter_build_memory_mb}
		\end{subfigure}
		\hfill
		\begin{subfigure}[t]{0.49\columnwidth}
			\centering
			\includegraphics[width=\linewidth]{figures/searchMem/range_memory_comparison.pdf}
			\caption{\footnotesize Search peak memory}
			\label{fig:rangeFilter_search_memory_mb}
		\end{subfigure}

		%		\caption{Time and space overhead of range filtering index construction}
%		\caption{Time and space overhead of index construction}
		\caption{\textcolor{violet}{Time and space overhead}}
		\label{fig:rangeFilter_build_index_comparison}
	\end{figure}
